### 2019-09-05 latex/machine_table.tex
added IBM Power 9 numbers

%\rowcolors{1}{white}{black!10!white}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{0.45\textwidth}{|c|>{\raggedright\arraybackslash}X|>{\raggedright\arraybackslash}X|}
\hline
Machine & Hardware & Compilers \\
\hline
    Apollo & NVIDIA TitanV & CUDA~10.1~(nvcc),\newline GCC~5.3.0 \\
Astra & Cavium Thunder-X2 CN9975-2000 & GCC~8.2~(ARM) \\ 
Blake & Intel(R) Xeon(R) Platinum 8160 & Intel~19.3.199, Intel~18.0.5 \\
Mutrino & Intel(R) Xeon(R) CPU E5-2698 v3 & Intel~18.0.5, GCC~8.2.0, Clang~9~(develop) \\
\hline
\end{tabularx}
\renewcommand{\arraystretch}{1.0}

>>>>

%\rowcolors{1}{white}{black!10!white}
\renewcommand{\arraystretch}{1.5}
\begin{tabularx}{0.45\textwidth}{|c|>{\raggedright\arraybackslash}X|>{\raggedright\arraybackslash}X|}
\hline
Machine & Hardware & Compilers \\
\hline
    Apollo & NVIDIA TitanV & CUDA~10.1~(nvcc),\newline GCC~5.3.0 \\
Astra & Cavium Thunder-X2 CN9975-2000 & GCC~8.2~(ARM) \\ 
Blake & Intel(R) Xeon(R) Platinum 8160 & Intel~19.3.199, Intel~18.0.5 \\
Mutrino & Intel(R) Xeon(R) CPU E5-2698 v3 & Intel~18.0.5, GCC~8.2.0, Clang~9~(develop) \\
Waterman & IBM Power9 10C 80HT & GCC~7.3.0 \\
\hline
\end{tabularx}
\renewcommand{\arraystretch}{1.0}
